Self Regulation Ontology Retest Analyses

### 2018-10-15 code/SRO_Retest_Analyses.Rmd
refactoring

source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Workspace.R')

test_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Complete_03-29-2018/'

retest_data_path = '/Users/zeynepenkavi/Documents/PoldrackLabLocal/Self_Regulation_Ontology/Data/Retest_03-29-2018/'
```

@@

```{r message=FALSE}
tmp = lit_review[duplicated(lit_review$reference)==FALSE,]

nrow(tmp)
sum(tmp$sample_size)
nrow(lit_review)
```

@@

```{r warning= FALSE, message =FALSE, echo=FALSE}
p1_legend = lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape=type))+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"),
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') +
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))

p1 = lit_review %>%
  filter(task == 'task') %>%
ggplot(aes(y = var, x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape = type), color='#00BFC4')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"),
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80"),
        legend.position = 'bottom') +
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 16, 17, 3))

p2 = lit_review %>%
  filter(task == 'survey') %>%
ggplot(aes(y = var, x = retest_reliability)) +
  geom_point(aes(size=sample_size, shape = type), color = '#F8766D')+
  facet_grid(task_group~., switch = "y", scales = "free_y", space = "free_y") +
  theme(panel.spacing = unit(0.5, "lines"),
        strip.placement = "outside",
        strip.text.y = element_text(angle=180),
        panel.background = element_rect(fill = NA),
        panel.grid.major = element_line(colour = "grey80")) +
  xlab("")+
  ylab("")+
  scale_x_continuous(limits = c(-0.25,1), breaks=c(-0.25, 0, 0.25, 0.5, 0.75, 1))+
  scale_shape_manual(breaks = sort(lit_review$type), values = c(15, 17, 3))

mylegend<-g_legend(p1_legend)

ggsave('Lit_Review_Plot.jpg', plot = p3, device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 24, height = 20, units = "in", dpi=100)
rm(p1, p2, p3, p1_legend, mylegend)
```

>>>>

source('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/code/SRO_Retest_Analyses_Workspace.R')
```

@@

```{r message=FALSE}
tmp = lit_review[duplicated(lit_review$reference)==FALSE,]
```

The literature review included `r nrow(tmp)` papers, `r sum(tmp$sample_size)` participants and `r nrow(lit_review)` data points on reliability.

@@

```{r warning= FALSE, message =FALSE, echo=FALSE}
